\section{Design preferences}


\subsection{Consistency}

The reflection facility as a whole
should be consistent, instead of being composed of ad-hoc, individually
designed parts.

\subsection{Reusability}

The provided metadata should be reusable
in many situations and for many different purposes, not only
for the obvious use cases. This is closely related to {\em completeness} (below).

\subsection{Flexibility}

The basic reflection and the libraries
built on top of it should be designed
in a way that they are eventually usable during both compile-time
and run-time and under various paradigms (object-oriented, functional, etc.),
depending on the application needs.

\subsection{Encapsulation}

The metadata should be accessible through conceptually well-defined interfaces.
The metadata should not be exposed directly to the used by compiler built-ins, etc.

\subsection{Stratification}

Reflection should be non-intrusive,
and the meta-level should be separated from the base-level language
constructs it reflects. Also, reflection should not be implemented
in a all-or-nothing manner. Things that are not needed, should not generally
be compiled-into the final application.

\subsection{Ontological correspondence}

The meta-level facilities should
correspond to the ontology of the base-level C++ language constructs
which they reflect. This basically means that all existing language
features should be reflected and new ones should not be invented.
This rule may have some important exceptions, like the reflection of
containers. 

\subsection{Completeness}

The proposed reflection facility should
provide as much useful metadata as possible, including various specifiers,
(like constness, storage-class, access, etc.), namespace members,
enumerated types, iteration of namespace members and much more.

\subsection{Ease of use}

Although reflection-based metaprogramming
allows to implement very complicated things, simple things
should be kept simple.

\subsection{Cooperation with rest of the standard and other librares}

Reflection should be
usable with the existing introspection facilites (like \verb@type_traits@)
already provided by the standard library and with other libraries.
