\section{Rationale}

This section explains some of the design decisions behind this proposal and
answers several frequently asked questions.

\subsection{Why metaobjects, why not reflect directly?}

{\textbf Q:}{\em Why should we define a set of metaobject concepts, let the compiler generate
models of these concepts and use those to obtain the metadata? Why not just extend the existing
type traits?}

{\textbf A:} The most important reason is the completeness and the scope of reflection.
Type traits (as they are defined now) work just with types. A reflection facility should
however provide much more metadata.
It should eventualy be able to reflect namespaces, functions, constructors, inheritance, variables, etc.

For example:

\begin{minted}{cpp}
pair<long, string> my_var;

// OK, we can print the name of the type of a variable:
cout << type_name<decltype(my_var)>() << endl;
// But we really, really want to print the name of the variable
// (without the use of the preprocessor)
cout << type_name<my_var>() << endl; // Error
// similar with namespaces:
cout << type_name<std::chrono>() << endl; // Error
// etc.
\end{minted}


Doing reflection with type traits limits the scope, because of the rules defining what
can be a template parameter. This rules could be updated to allow for example an expression
representing a particular class constructor to  be passed as a template argument.
Also currently there is no expression for specifying (not invoking) a constructor
or a particular function overload, so additional rules would have to be added.

This would (in our opinion) be a much more drastic change to the standard, than
the adoption of this proposal. If expressions denoting a namespace or a particular
constructor or a function overload were added just for the purpose of reflecting
them (with the \verb@mirrored@ keyword), then all the changes could be localized
in the reflection subsystem and remain invalid in rest of the language:

\begin{minted}{cpp}
mirrored(std::current_thread); // OK - MetaNamespace
std::current_thread; // error - not a primary expression

mirrored(std::sin); // OK - MetaOverloadedFunction
std::sin; // error - cannot resolve overload

mirrored(std::sin(double)); // OK - MetaFunction
std::sin(double); // error - invalid expression
//etc.
\end{minted}


Second reason is access to private and protected members. There are many use-cases where
access to non-public class members through reflection is desired. If reflection was
done through type traits directly on the class members, it would be either impossible
to reflect non-public members or the access rules would have to be changed to somehow
allow access in reflection expressions:

\begin{minted}{cpp}
class C
{
private:
	typedef int T;
public:
};

assert(some_trait<C::T>::value); //OK, we are reflecting so we have access
\end{minted}

but not outside:

\begin{minted}{cpp}
C::T x = 0; // Error, C::T is private
\end{minted}

With the reflection operator like \verb@mirrored(X)@, the access rules would have
to be updated only to allow the reflection operator to have access to everthing.
At the first glance, the following two expressions;

\begin{minted}{cpp}
some_trait<C::T>::value
\end{minted}

and

\begin{minted}{cpp}
mirrored(C::T)
\end{minted}

look similar and so the changes to the access rules could seem similar too, but
that is not the case. The (single) \verb@mirrored@ operator would have special status,
on the other hand type traits are regular templates (with some magic inside) and
all (several dozens of them) would need to be distinguished from all the other templates
in the \verb@std@ namespace, which should not have private access.

Having said that, we do not object to extending the type traits where it does make sense.

One other reason for having a new reflection operator is, that there already is an
existing (very limited) reflection operator, namely \verb@typeid@ which "returns"
a compiler-generated "metaobject" -- \verb@std::type_info@. We are aware that there
are differences between \verb@typeid@ and \verb@mirrored@, but the basic idea is similar.

\subsection{Why are the metaobjects anonymous?}

{\textbf Q:}{\em Why should the metaobjects be anonymous types as opposed to
types with well defined and standardized names or concrete template classes, (possibly with some
special kind of parameter accepting different arguments than types and constants)?}

{\textbf A:} We wanted to avoid defining a specific naming convention, because it would
be difficult to do so and very probably not user friendly (see C++ name mangling). There
already are precedents for anonymous types -- for example C++ {\em lambdas}.

Another option would be to define a concrete set of template classes like:

\begin{minted}{cpp}
namespace std {

template <typename T>
class meta_type /* Model of MetaType */
{ };

}
\end{minted}

which could work with types, classes, etc., but would not work with namespaces, constructors,
etc. (see also the Q/A above):

\begin{minted}{cpp}
namespace std {

template <something X> //<- Problem
class meta_constructor /* Model of MetaConstructor */
{ };

template <something X> //<- Problem
class meta_namespace /* Model of MetaNamespace */
{ };

}

typedef std::meta_namespace<std> meta_std; //<- Problem
\end{minted}

Instead of this, the metaobjects are anonymous and their (internal) identification
is left to the compiler. From the user's point of view, the metaobject can be distinguished
by the means of the metaobject traits and tags as \hyperref[section-current-Concepts]{described above}.

\subsection{Why this rendering of metaobjects?}

{\textbf Q:}{\em Why were the metaobject concepts from n3996 transformed into a set
of types with external template classes operating on them?
}

{\textbf A:} N3996 defined a set of abstract metaobject concepts including their
instances, traits, attributes and functions.
Then two possible concrete transformations into valid C++ were shown in the appendices.

\begin{enumerate}
\item Structures where the attributes were constexpr static member variables and the functions were
constexpr static member functions.
\item Types where the traits, attributes and functions are implemented as specializations of
class templates defined on namespace-level.
\end{enumerate}

In N4111 the second option was picked for several reasons:

\begin{itemize}
\item It is closer to standard type traits and to popular metaprogramming libraries like {\em Boost.MPL}, etc.
\item It should require less resources and time to compile, since the implementation of various
metafunctions (class templates) like \verb@base_name@, \verb@scope@ or \verb@position@ and
especially those returning \concept{MetaobjectSequence}s, like \verb@members@, \verb@overloads@,
\verb@base_classes@ etc. for concrete metaobjects can be instantiated individually
and need to be instantiated only if they are actually used in the code. It would probably be harder
to do so if they were implemented as (non-template) class members.
\end{itemize}

\subsection{Should reflection have access to private members?}

Some concerns were raised about the potential misuse of reflection to
bypass the class member access restrictions. This is a valid point, but
there are several different ways to achieve this if the programmer
wants to and we feel that restricting reflection only to public class members
would severly limit its usefulness.
