\subsection{Basic overview}

In P0194R0 we propose to add native support for
compile-time reflection to C++ by the means of lightweight, compiler-generated
types -- {\em metaobjects}, providing \hyperref[term-metadata]{metadata}
describing various \hyperref[term-base-meta-level]{base-level} program declarations.

The metaobjects exist only at the type-level, they do not have any constructors
or members and cannot be instantiated\footnote{It's not possible to define
a run-time variable of metaobject type}.

Their sole purpose is to give a \hyperref[term-first-class]{first class identity}
to the reflected entity\footnote{Namespace, typedef, function, parameter, specifier, etc.},
so that we can pass it as argument or return value in metaprograms and to
separate the reflection of a declaration from the querying of metadata.

The metadata can be obtained from a metaobject by using one of the class templates
which comprise its interface.
Since there are many different kinds of
base-level reflectable declarations, the metaobjects reflecting them are
modeling various {\em metaobject concepts}. The metaobjects can be inspected
by {\em metaobject traits}, which indicate whether a metaobjects has or has
not a particular property or if is falls into a particular category.

We introduce a new reflection operator -- \verb@reflexpr@ which returns a
metaobject type reflecting its operand.

For example:

\begin{minted}{cpp}
typedef reflexpr() meta_global_scope;
typedef reflexpr(int) meta_int;
typedef reflexpr(std) meta_std;
typedef reflexpr(std::size_t) meta_std_size_t;
typedef reflexpr(std::thread) meta_std_thread;
typedef reflexpr(std::pair) meta_std_pair;
\end{minted}

P0194R0 also defines the initial subset
of metaobject concepts which we assume to be essential
and which will provide a good starting point for future extensions.

When finalized, the metaobjects can be together with some additions
to the standard library, used to implement other third-party libraries
providing both compile-time and run-time, high-level reflection.

