\section{Experimental implementation}

A fork of the clang compiler with a initial, partial, experimental implementation
of this proposal can be found on github \cite{clang-reflexpr-impl}.
The modified compiler can be built by following the instructions listed
in \cite{clang-getting-started}, but instead of checking out the official clang
repository, the sources on the \texttt{mirror-reflection} branch of the modified
repository should be used.

The implementation required changes (mostly additions) to roughly 3500 lines
of code in the compiler plus circa 540 lines in the \texttt{<reflexpr>} header.

All examples listed in Appendix \ref{section-reflexpr-examples} are working with
the modified compiler.

This particular implementation works by generating and adding new \texttt{CXXRecordDecl}s,
with member typedefs and member constants providing basic meta-data, to the AST.
The templates implementing the metaobject operations are referencing and
occasionally transforming the members of the metaobject types.

The \texttt{is\_metaobject} trait is implemented by extending the existing
clang's type-trait framework and adding the \texttt{\_\_is\_metaobject} builtin
operator.

The \meta{ObjectSequence} operations, namely \texttt{get\_size} and
\texttt{get\_element} are implemented lazily by using the new
\texttt{\_\_reflexpr\_size} and \texttt{\_\_reflexpr\_element} operators.

Note that the limited time between the committee meetings and out limited experience
at hacking clang internals at the time of starting with the fork,
lead to the implementation not being lazy and thus neglecting some important
opportunities to do optimizations. We expect that the compiler implementers
or ourselves during our next attempts will do a better job.

Also note that P0194R0 underwent some last-minute changes,
which were not incorporated into the implementation yet.
