\section{Revision history}

\subsection{P0385R0}

The initial revision of the design paper accompanying the P0194 papers.

\subsection{P0385R1}

This revision brought the following updates reflecting
the changes made in the P0194R2 paper.

\begin{itemize}
\item Based on the feedback from Oulu, the specification of typedef and
type alias reflection has been simplified. We no longer require reflection
to be aware of the whole chain of type aliases especially not in the context
of templates, each type alias only references the underlying type with unique
identity at the base level.
\item Unlike in the previous revision it is now possible to create variables
with {\em metaobject} types.
\item Section~\ref{fac-for-each} describing the \verb@for_each@ function
planned to be included in future revisions has been revised.
\item The {\em reverse reflection operator} has been renamed to \verb@unreflexpr@.
\item The {\em identifier-generating operator} has been renamed to \verb@idreflexpr@.
\item The mechanism for enumerating public-only vs. all (including non-public ones)
class members has been changed. Now the \say{basic} operations like
\verb@get_data_members@, \verb@get_member_types@, etc.
return all members, and the \verb@get_public_data_members@,
\verb@get_public_member_types@, return only the public class members.
\item All examples have been revised and extended according to the changes listed above.
\item New examples have been added to section~\ref{design-prefs} describing
the design considerations.
\item A description of the implementation has been added (section~\ref{implementation}).
\item A brief introduction to the {\em Mirror reflection utilities} has been added
(section~\ref{mirror-lib}).
\end{itemize}

\subsection{P0385R2 -- current revision}

We have made several big changes in revision R3 of the P0194 paper:

\begin{itemize}
\item We introduced the \verb@$@ character to the basic source character set
	as a prefix for all reflection-related operators -- both the primary
	reflection operator which is already part of the wording and for
	any which may be added in the future.
\item The reflection-related operators have been renamed
	\begin{itemize}
	\item from \verb@reflexpr@ to \verb@$reflect@,
	\item from \verb@unreflexpr@ to \verb@$unreflect@ and
	\item from \verb@idreflexpr@ to \verb@$identifier@.
	\end{itemize}
\item The reflection-related namespace has been renamed from \verb@std::meta@
	to \verb@std::reflect@ in order to avoid confusion and conflicts with
	any potential metaprogramming library which could be added in the future.
\item The reflection-related header file has been renamed from \verb@<reflexpr>@
	to \verb@<reflect>@.
\item Direct reflection of specifiers (previously \verb@reflexpr(public)@)
	and metaobjects reflecting specifiers (conforming to the \verb@Specifier@
	concept) have been removed temporarily and their functionality has been
	partially replaced with boolean traits.
\item The metaobject concept hierarchy has been slightly changed; in addition
	to the \verb@Specifier@, the \verb@TagType@ concept has
	also been removed, its operations were taken over by \verb@Enum@
	and \verb@Record@ concepts. The \verb@Reversible@ concept has also
	been removed for the time being.
\item The order of template parameters for \verb@MetaSequence@ operations has
	been matched to similar operations of \verb@std::tuple@.
\item The suffix \verb@_m@ was reverted back to \verb@_t@ for all
	metaobject-returning operations.
\end{itemize}

In this revision of P0385 we made the following changes:

\begin{itemize}
\item Some of the use-cases were removed for the sake of brevity, please see
	the previous revisions of this paper.
\end{itemize}

